NHF1 Deamination Sequence and Position Figure Generation

### 2022-07-11 R/NHF1DeaminationAnchoredExcisionSiteDataGeneration.rmd
Third generation of figure plots
- Updated plotting notebook
- Added parameters to plotting functions where necessary, such as axis labels or limits.
- Added TG-filtering option in NHF1 notebooks.

---
title: "NHF1 Deamination Anchored Excision Site Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

>>>>

---
title: "NHF1 Deamination Anchored Excision Site Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered, TG_filtered]
---

### 2022-07-11 R/NHF1DeaminationAnchoredExcisionSiteFigureGeneration.rmd
Third generation of figure plots
- Updated plotting notebook
- Added parameters to plotting functions where necessary, such as axis labels or limits.
- Added TG-filtering option in NHF1 notebooks.

---
title: "NHF1 Deamination Anchored Excision Site Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

>>>>

---
title: "NHF1 Deamination Anchored Excision Site Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered, TG_filtered]
---

### 2022-07-11 R/NHF1DeaminationSequenceAndPositionDataGeneration.rmd
Third generation of figure plots
- Updated plotting notebook
- Added parameters to plotting functions where necessary, such as axis labels or limits.
- Added TG-filtering option in NHF1 notebooks.

---
title: "NHF1 Deamination Sequence and Position Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

>>>>

---
title: "NHF1 Deamination Sequence and Position Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered, TG_filtered]
---

### 2022-07-11 R/NHF1DeaminationSequenceAndPositionFigureGeneration.rmd
Third generation of figure plots
- Updated plotting notebook
- Added parameters to plotting functions where necessary, such as axis labels or limits.
- Added TG-filtering option in NHF1 notebooks.

---
title: "NHF1 Deamination Sequence and Position Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

>>>>

---
title: "NHF1 Deamination Sequence and Position Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered, TG_filtered]
---
